Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Discussion

* ...

Grounded theory may not be able to provide a single generally applicable model
for transformation, at least not in a literature review made based on the
current agile transformation publications. This is because of two things.
First, the organizations seem to differ too much from each other. Secondly, the
published studies focus too much on isolated phenomena within the larger
transformation.
It would require too big of an interpretation to combine all the various cases
into one theoretical model. We have chosen to present transformations using an
elementary two-axial classification of transformations, and listings of
individual phenomena that typically occur in a transformation.

@@

@@

* Transformation and scaling up are connected concepts. Although this research
  focuses on transformation process only, it can not be completely separated
  from discussion on scaling up, or on large-scale agile implementation in
  general.

@@

@@

>>>>

Grounded theory may not be able to provide a generally applicable models for
agile transformation, at least not in a literature review made based on the
current agile transformation publications. This is because of two things.
First, the organizations seem to differ too much from each other. Secondly, the
published studies focus too much on isolated phenomena within the larger
transformation.
It would require too big of an interpretation to combine all the various cases
into one theoretical model. For these reasons we chose to present
transformations using an elementary two-axial classification of transformations,
and listings of individual phenomena that typically occur in a transformation.

% Transformation and scaling up

Transformation and scaling up are related concepts. Although this research
focuses on transformation process only, it can not be completely separated from
discussion on scaling up, or on large-scale agile implementation in general.
Examples on where scaling up can be seen as the transformation itself are
organizations which start with a successful pilot project, after which agile
methods are introduced step wise to the rest of the organization.

% ------------------------------

% Comparison with literature

\citet{Misra2010} states that an agile adoption requires a change in mindset.
--> What evidence on this was there?

The higher level of coordination required in a large organization compared to
ideal small agile organizations was showing.

@@

% Related challenges and success factors

@@

% ?

@@

% Defence against criticism for weak evidence in primary studies

@@

% Different organizations

% Other ?
